The ChEMBL database as Linked Open Data

### 2012-04-02 article.tex
Written a full abstract

\begin{abstract}
This paper describes the continued conversion of ChEMBL data into RDF triples, using a few existing
ontologies, and demonstrates a few new use cases, taking advantage of its linked nature.
\end{abstract}

>>>>

\begin{abstract}
Making data available as RDF has the advantages that integration with other web resources brings:
we can link out to related data, others can link to this data, it makes the data machine readable,
is easy to extend with additional information,  and enables a representation of the data in common
vocabularies. This combination provides a clear, open interface.
This paper describes the continued conversion of data from the ChEMBL database into RDF triples.
This updated version of ChEMBL-RDF now uses recently introduced, such as the CHEMINF and CiTO ontologies,
exposes more information from the database, and is now available as dereferencable, linked data.
To demonstrate the new features, we here present a few new use cases, showing integration with
other web resources using semantic web technologies.
\end{abstract}
